---
title: "Reanalysis- Flexible Force"
output: 
  html_document:
    code_folding: hide
    authors: Claudia Ramos, Noah Auger
---

```{r setup,include=TRUE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE)
```

## Steps

The first step to analyzing any data in R is to upload it into your working environment.
These results are a sneak peek into each data set detailing the first few cell lines.
```{r environment}
 summarizedPharmacoData <- readRDS("C:/Users/claudia/Desktop/Replicathon/data/summarizedPharmacoData.rds")
 modelSummarizedPharmacoData <- readRDS("C:/Users/claudia/Desktop/Replicathon/data/modelSummarizedPharmacoData.rds")
 rawPharmacoData <- readRDS("C:/Users/claudia/Desktop/Replicathon/data/rawPharmacoData.rds")
head(unique(rawPharmacoData$cellLine))
head(unique(modelSummarizedPharmacoData$cellLine))
head(unique(summarizedPharmacoData$cellLine))
```

## Does the number of dosages affect the results?

The number of dosages limits the amount of data and the ranges in each study are highly different, hindering the correlations resulting in "unaccurate" results.
#The code is telling us which concentrations were used in each study and plotting it visibly in a histogram

```{r concentrations}
tapply(rawPharmacoData$concentration, rawPharmacoData$study, function(x) {length(unique(x)) })
DrugConcentrations <- tapply(rawPharmacoData$concentration, rawPharmacoData$study, function(x) {unique(x) })
DrugConcentrations
DrugConcentrations$CCLE
range(DrugConcentrations$CCLE)
range(DrugConcentrations$GDSC)
hist(DrugConcentrations$GDSC)
 hist(DrugConcentrations$CCLE)
```
# x shows the percentage of viablity from 0-175, the y is showing the density of cells that correspond to the viability percentage

```{r,include=TRUE}
library(tidyverse)
rawPharmacoData %>%
    summarize(min_viability = min(viability),
              max_viability = max(viability),
              n_too_small   = sum(viability < 0),
              n_too_big     = sum(viability > 100))

rawPharmacoData %>%
    ggplot(aes(x = viability, group = study, fill = study, color = study)) +
    geom_density(alpha = 1/4) +
    xlim(0, 170) +
    ggtitle("Distributions of viability scores by study")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


##The sum of viabilty percentage points between 0-100. Its showing total amount of cell lines, meaning the drug-resistant cells


## Range and values between 0-100
```{r,include=TRUE}
range(rawPharmacoData$viability)
sum(rawPharmacoData$viability < 0)
sum(rawPharmacoData$viability > 100)
```



```{r, include=TRUE}
summarizedPharmacoData %>%
    ggplot(aes(x = (auc_GDSC), y = (auc_CCLE))) +
     geom_point(alpha = 1/2, cex = 1/2) + 
     facet_wrap(~ drug) +
     xlab("(GDSC AUC)") +
     ylab("(CCLE AUC)") +
     ggtitle("AUC summaries of cell line response across studies")
```

# Correlation coefficient comparison
###7 Nilotinib        0.772      0.147  

```{r, include=TRUE}
## with the tidyverse
drugCorrsIC50 <- summarizedPharmacoData %>% 
    group_by(drug) %>%
    summarize(Pearson_ic50  = cor(-log10(ic50_GDSC / 10^6), -log10(ic50_CCLE / 10^6), method = "pearson"),
              Spearman_ic50 = cor(-log10(ic50_GDSC / 10^6), -log10(ic50_CCLE / 10^6), method = "spearman"))


drugCorrsAUC <- summarizedPharmacoData %>% 
    group_by(drug) %>%
    summarize(Pearson_auc  = cor((auc_GDSC / 10^6),(auc_CCLE / 10^6), method = "pearson"),
              Spearman_auc = cor((auc_GDSC / 10^6),(auc_CCLE / 10^6), method = "spearman"))

drugCorrsAUC

drugCorrsIC50 <- gather(drugCorrsIC50, measure, correlation, -drug)
drugCorrsAUC <- gather(drugCorrsAUC, measure, correlation, -drug)


drugCorrsIC50 %>%
    ggplot(aes(x = drug, y = correlation, fill = measure, group = measure)) +
    geom_bar(stat = "identity", position = position_dodge(), colour = "black") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_fill_grey() +
    ylim(0, 1) + 
    ggtitle("Correlation of cell line IC50 summaries between studies for each drug")

drugCorrsAUC %>%
     ggplot(aes(x = drug, y = correlation, fill = measure, group = measure)) +
     geom_bar(stat = "identity", position = position_dodge(), colour = "black") + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
     scale_fill_grey() +
     ylim(0, 1) + 
     ggtitle("Correlation of cell line AUC summaries between studies for each drug")
```

